Figure 6. Differential Protein expression

### 2022-01-31 reports/rmarkdown/manuscript/Figure6.Rmd
Updating to accomodate Paulos new code in niceRplots

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(rstatix)
  library(niceRplots)
})  })  })

@@

    ## Heatmap
    par(mar=c(4,.2,2.5,2.5)) #(bottom, left, top, right) 
    image( t(top_PROT_mfi[h$order,pull(df, "ID")][nrow(top_PROT_mfi):1,]),
           col = colorRampPalette(c("navy","navy","grey95","firebrick4","firebrick4") )(99),
           breaks = breaks,
           axes=F)
    mtext( "Differentialy Expressed Proteins", side=3, las = 1, cex = .7, line =1.5,xpd=T)
    mtext( c("Study Groups"), side=1, las = 1, cex = .7, line = 1,xpd=T)

@@

  # select only sig. cytokines 
  sig <- df_krusk %>% filter(p.adj<0.05) %>% pull(Cytokines)
  sig_df <- cytokine_data_log[sig,samples_use$ID] %>%
    cbind(Max = c(rep(max(.)+n, nrow(.))))

  groupings <- samples_use[[group]] [ match( colnames(sig_df[,1:ncol(sig_df)-1]) , as.character(samples_use$ID)  ) ]
  groupings <- c(groupings, "Max")

@@

# Luminal Cytokine plot 
g <- c("IL1a", "MIG", "IP10", "IL1b", "IL12_p70", "MCP1")
Luminal <- sig_stars.fun(s$Kruskal_Luminal_gr, s$`Dunn's_Luminal_gr`, "Luminal_gr", order = g)
temp <- as.factor(c(Luminal$groupings, "Max"))
stars <- Luminal$stars_df

par( mar=c(1.4,5,1.5,0)) #b,l,t,r 
violist(data=Luminal$sig_df,
          srt=45,
          genes= g,
          col = pal, transparency = 50,
          clustering=c(Luminal$groupings),smooth = 2 )
segments(x0 = stars$line_x0, x1 = stars$line_x1, y0 = stars$y_, y1 = stars$y_) 
text( stars$x , stars$y_+.05,
        labels = stars$p.adj.signif, srt = 0, xpd = TRUE, cex=1)
title(main = "Luminal gr. Cytokines", line = 0.7, cex.main = .9)

rect(7, -0.5, 5.5, par("usr")[2], density = NULL, angle = 45, xpd = TRUE,
     col = "White", border = "White", lty = par("lty"), lwd = par("lwd")
     )

@@

# Tissue Cytokine plot
Tissue <- sig_stars.fun(s$Kruskal_Tissue_gr, s$`Dunn's_Tissue_gr`, "Tissue_gr")
temp <- factor(Tissue$groupings, levels=c("T1","T2","T3","T4","Max"))
stars <- Tissue$stars_df

par( mar=c(24.4,6,1.5,0)) #b,l,t,r
violist(data=Tissue$sig_df,
          srt=45, 
          genes= rownames(Tissue$sig_df),
          col = pal, transparency = 50,
          clustering=Tissue$groupings, smooth = 2 )
segments(x0 = stars$line_x0, x1 = stars$line_x1, y0 = stars$y_, y1 = stars$y_) 
text( stars$x , stars$y_+.05,
        labels = stars$p.adj.signif, srt = 0, xpd = TRUE, cex=1)
title(main = "Tissue gr. Cytokines", line = 0.7, cex.main = .9)

rect(6, -0.5, 4.5, par("usr")[2], density = NULL, angle = 45, xpd = TRUE,
     col = "White", border = "White", lty = par("lty"), lwd = par("lwd")
     )
add_letter("d")

@@

# side by side unscaled
plot_grid(ggdraw(p.plot),ggdraw(p.plot_T), 
          labels = c('a', 'b'),rel_widths=c(1,1), greedy = F) # , 'c', 'd'

>>>>

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(rstatix)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

@@

    ## Heatmap
    par(mar=c(4,.2,2.5,2.5)) #(bottom, left, top, right) 
    image( t(top_PROT_mfi[h$order,pull(df, "ID")][nrow(top_PROT_mfi):1,]),
           col = colorRampPalette(c("navy","navy","grey95","firebrick4","firebrick4") )(99),
           breaks = breaks,
           axes=F)
    mtext( "Differentialy Expressed Proteins", side=3, las = 1, cex = .7, font = 2, line =1.5,xpd=T)
    mtext( c("Study Groups"), side=1, las = 1, cex = .7, line = 1,xpd=T)

@@

  # select only sig. cytokines 
  sig <- df_krusk %>% filter(p.adj<0.05) %>% pull(Cytokines)
  sig_df <- cytokine_data_log[sig,samples_use$ID]

  groupings <- samples_use[[group]] [ match( colnames(sig_df[,1:ncol(sig_df)-1]) , as.character(samples_use$ID)  ) ]
  groupings <- c(groupings)

@@

# Luminal Cytokine plot 
g <- c("IL1a", "MIG", "IP10", "IL1b", "IL12_p70", "MCP1")
Luminal <- sig_stars.fun(s$Kruskal_Luminal_gr, s$`Dunn's_Luminal_gr`, "Luminal_gr", order = g)
stars <- Luminal$stars_df

par( mar=c(1.4,5,1.5,2)) #b,l,t,r 
violist(data=Luminal$sig_df,
          srt=45, y_padding = 2, smooth = .2,
          genes= g, #add_ylims = T, #gives starting value of y-axis and max value of all data points
          col = pal, transparency = 50,
          clustering=c(Luminal$groupings))
segments(x0 = stars$line_x0, x1 = stars$line_x1, y0 = stars$y_, y1 = stars$y_) 
text( stars$x , stars$y_+.05,
        labels = stars$p.adj.signif, srt = 0, xpd = TRUE, cex=1)
title(main = "Luminal gr. Cytokines", line = 0.7, cex.main = .9)

@@

# Tissue Cytokine plot
Tissue <- sig_stars.fun(s$Kruskal_Tissue_gr, s$`Dunn's_Tissue_gr`, "Tissue_gr")
stars <- Tissue$stars_df

par( mar=c(20.4,6,1.5,3)) #b,l,t,r
violist(data=Tissue$sig_df,
          srt=45, y_padding = 2, smooth = .2,
          genes= rownames(Tissue$sig_df), 
          col = pal, transparency = 50, #add_ylims = T,
          clustering=Tissue$groupings )
segments(x0 = stars$line_x0, x1 = stars$line_x1, y0 = stars$y_, y1 = stars$y_) 
text( stars$x , stars$y_+.05,
        labels = stars$p.adj.signif, srt = 0, xpd = TRUE, cex=1)
title(main = "Tissue gr. Cytokines", line = 0.7, cex.main = .9)

add_letter("d")

@@

# side by side unscaled
plot_grid(ggdraw(p.plot),ggdraw(p.plot_T), 
          labels = c('a', 'b'),rel_widths=c(1,1), greedy = F)
